Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-04-05 bbbq_article.tex
Review paper on 2021-04-05, progress #212

See tables \ref{tab:ncbi_counts_1} and tables \ref{tab:ncbi_counts_2}
for an overview of all amounts.
In table \ref{tab:ncbi_counts_1} one expects [RJCB: name these]
numbers to add up. 
The number of unique SNPs and unique gene names
does not add up for MAP and TMP,
as one SNP may work on multiple isoforms, some of which can be MAP
where others can be TMP.
The number of unique SNPs and unique gene names
does not add up for TMPs in TMH and TMP in soluble regions
as one SNP may work on multiple isoforms, some of which can be MAP
where others can be TMP, and some SNPs fall in a TMH, where others
are found in soluble regions
In table \ref{tab:ncbi_counts_2} one expects [RJCB: name these]
numbers to add up.

>>>>

See tables \ref{tab:ncbi_counts_1} and tables \ref{tab:ncbi_counts_2}
for an overview of all amounts.
In table \ref{tab:ncbi_counts_1} there are multiple instances where
the amounts are expected to add up, yet don't, as one SNP can work on
multiple isoforms. For example, there are 9,621 unique SNPs 
found in all proteins, of which 4,219 around found in MAPs 
and 6,026 in TMPs. Apparently, 624 SNPs work on a set of isoforms that
contains both MAPs and TMPs.
